Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-08-07 article/article.tex
critic update

	SATIE stands for \emph{laboratoire des Systèmes et Applications des Technologies de l'Information et de l'Energie} (Information and Energy Technology Systems and Applications Laboratory).\\
	Created in 1975 under the name \emph{Laboratoire d'Electricité de l'ENSET}, then renamed \emph{LESiR} in 1984 at the time of its association with CNRS, then finally SATIE in 2002, the laboratory studies

>>>>

	SATIE stands for \emph{laboratoire des Systèmes et Applications des Technologies de l'Information et de l'Energie} (Information and Energy Technology Systems and Applications Laboratory).\\
	Created in 1975 under the name \emph{Laboratoire d'Electricité de l'ENSET}, then renamed \emph{LESiR} in 1984 at the time of its association with CNRS, then finally SATIE in 2002, the laboratory covers a large field of study including signal processing, electronics, and energy conversion.\\

	The SATIE is linked to the following academic structures : ENS Paris-Saclay, ENS Rennes, Université Paris-Saclay, Cergy Paris Université, Université Gustave Eiffel, CNAM Paris and CNRS. It counts five geographical sites near the aforementioned structures.

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.7\linewidth]{src/sites_geoo_satie}
		\caption{Geographic sites of SATIE (copyright E. Vourc'h)}
		\label{fig:sitesgeoosatie}
	\end{figure}
